### 2024-11-02 project1/nsSurvey.tex
new

In our finite-sample experiments, we have observed that the actual computational cost to be significantly different from the theoretical complexity, as not only the order of complexity but also the constant factors can affect the computational cost.
In Figure~\ref{fig1:tcc}, the total computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32GB of RAM.
8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over the kNN.
The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
They are demanding in terms of memory.
For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
The KRR-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.

@@

Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$, excluding the simulation time.
The simulation time is omitted as it is the same for all procedures.
The remainder can be decomposed into two parts: hyperparameter tuning and model implementation.
The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters.
In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space grows with the simulation budget $\Gamma$.
The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.

>>>>

The cost associated with pooling makes a significant impact on the overall computaional complexity of a metamodel-based nested simulation procedure.
In our finite-sample experiments, we have indeed observed that the actual computational cost to deviate significantly from the simulation cost.
In Figure~\ref{fig1:tcc}, the total actual computational time of different nested simulation procedures for European call options and geometric Asian options with $d = 10$ is illustrated in a log-log scale.
The $x$-axis shows the total simulation budget $\Gamma$, and the $y$-axis is the total computational time for 1 replication of the numerical experiment, in seconds.
All procedures are implemented on a machine with an AMD Ryzen 9 7900X processor with 32GB of RAM.
8 cores are used for parallel computing, and the total computational time is the sum of the simulation time, the training time, and the prediction time.
The regression and kernel smoothing-based procedures are the most efficient among the metamodel-based procedures.
Since the regression-based procedure has a higher empirical rate of convergence, it is preferred over the kNN.
The likelihood ratio-based and KRR-based procedures are the most computationally expensive among all procedures.
They are also demanding in terms of memory.
For budgets larger than $10^5$, the likelihood ratio-based procedure becomes impractical as storage of the likelihood weights becomes a bottleneck.
The KRR-based procedure suffers from both cross-validation and inverting a kernel matrix of size $M \times M$.
To separate the total computational time into different attributes, we provide a detailed analysis of the total computational time in the remainder of this section.

@@

Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$.
The simulation time is omitted as it is the same for all procedures.
The remaining computations can be decomposed into two parts: hyperparameter tuning and model implementation.
The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters.
In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space grows with the simulation budget $\Gamma$.
The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
